---
title: |
  | APLD STAT MTD BIOMED INFORMTCS
  | Assignment 3
author: "Tianchuan Gao"
date: "2023-09-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1
### (a)
$$
E[X] = 100*0.13 = 13
$$
Therefore, the expected number of smokers in a random sample of 100 students from this university is **13**

### (b)

## Question 2
### (a)
```{r}
1-pnorm(83,77,5)
```
the probability of observing an 83F temperature or higher in LA during a randomly chosen day in June is **0.115 **

### (b)
```{r}
qnorm(.1,77,5)
```
temperature of the coldest 10% of the days during June in LA is **70.59**

## Question 3
### (a)
$X \sim bin(15,0.45)$  
$\mu = np = 15*0.45 = 6.75$  
$\sigma = \sqrt{np(1-p)} = \sqrt{15*0.45*0.55} = 1.93$  
expected value is **6.75** and standard deviation is **1.93**

### (b)
$X \sim bin(15,0.08)$ 
```{r}
1-dbinom(0, 15, .08)-dbinom(1, 15, .08)-dbinom(2, 15, .08)
```
the probability that 3 or more of the people in this sample could donate blood to a patient with Type O- blood is **0.113**

## Question 4
$X \sim bin(250,0.3)$ 

### (a)
```{r}
dbinom(60,250,.3)
```
the probability that exactly 60 stocks are infected is **0.006**

### (b)
```{r}
pbinom(60,250,.3)
```
the probability that at most 60 stocks are infected is **0.021**

### (c)
```{r}
sum(dbinom(80:250, 250, 0.3))
```
the probability that at least 80 stocks are infected is **0.265**

### (d) 
```{r}
pbinom(100,250,.3)
```
take a random sample of 250 is reasonable

## Question 5
### (a)
```{r}
1-pnorm(2.6)
```
the probability that an outcome Z is greater than 2.60 is **0.005**

### (b)
```{r}
pnorm(1.35)
```
the probability that Z is less than 1.35 is **0.911**

### (c)
```{r}
pnorm(3.1) - pnorm(-1.7)
```
the probability that Z is between -1.70 and 3.10 is **0.954**

### (d)
```{r}
qnorm(0.85)
```
cuts off the upper 15% of the distribution is **1.036**

### (e)
```{r}
qnorm(0.2)
```
the lower 20% of the distribution is **-0.842**

## Question 6
### (a)
```{r}
1 - pnorm(4948, 4313, 583)
```
**13.8%** of the triathletes in the group did he finish faster than

### (b)
```{r}
1 - pnorm(5513, 5261, 807)
```
**37.7%** of the triathletes in the group did she finish faster than

### (c)
```{r}
qnorm(0.05, 4313, 583)
```
cutoff time for the fastest 5% of athletes in the men’s group is **3354**

### (d)
```{r}
qnorm(0.9, 5261, 807)
```
cutoff time for the slowest 10% of athletes in the women’s group is **6295**

## Question 7
### (a)

### (b)
Yes, these data appear to follow a normal distribution.  
points follow the line on the normal probability plot.

## Question 8
### (a)
$\lambda = 1,  \mu = \lambda = 1, \sigma = \sqrt{\lambda} = 1$  
the mean is **1** and the standard deviation is **2**

### (b)
```{r}
ppois(3, lambda = 1)
```
the probability that this stenographer makes at most 3 typos in a given hour is **0.981**

### (c)
```{r}
1 - ppois(4, lambda = 3)
```
the probability that this stenographer makes at least 5 typos over 3 hours is **0.185**

## Question 9
### (a)
$P(blue^{c})*P(blue^{c})*P(blue) = 0.875 * 0.875 * 0.125 = 0.096$

### (b)
average number of children a pair of parents would have before having a blue-eyed child follows Geometric distribution  
$\mu = 1/p = 8$  
**8** children would such a pair of parents have before having a blue-eyed child  
$\sigma = \sqrt{(1-p)/p^2} = 7.483$  
the standard deviation of the number of children they would expect to have until the first blue-eyed child is **7.483**  

## Question 10
### (a)
**42** entries are in the table for the joint distribution of X and Y  
**15** entries are 0  

### (b)
$$P(X=1 ; Y=0) = 1/6 * 1/2 = 1/12$$  

### (c)
$$P(X=1 ; Y=2) = 0$$  

### (d)
$$P(X=6 ; Y=3) = 1/6 * \left(\begin{array}{l}6 \\ 3\end{array}\right) .5^3*.5^3 =  0.052$$  

